The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-12 rockerverse.Rmd
Full citation on first mention of googleCloudRunner
also one sentence per line and consistent use of -based and -related

>>>>

**\CRANpkg{googleCloudRunner}** is an interface with [Google Cloud Platform](https://cloud.google.com/) container-related services, with tools to make it easier for R users to interact with them for common use cases \citep{cran:googleCloudRunner}.
It includes deployment functions for creating R APIs using the Docker-based [Cloud Run](https://cloud.run) service.
Users can create long running batch jobs calling any Docker image including Rocker via [Cloud Build](https://cloud.google.com/cloud-build/) and schedule services using [Cloud Scheduler](https://cloud.google.com/scheduler/).
